---
title: "esm206_lab7"
author: "Jessica West"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, results = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(kableExtra)
library(modelsummary)
library(stargazer)
library(devtools) # I added
library(calecopal) # I added
```

## Explore Penguins

Use `GGally:ggpairs90` to create a pairs plot.

```{r}
ggpairs(penguins)   # shows various graphs explaining variable relationships
```

That's kind of overkill- let's simplify the variables that we include in our ggpairs plot:

-species
-bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species)) +
  scale_fill_manual(values = cal_palette("oak"))
```

## Multiple Linear Regression

We are going to try and understand the relationship between multiple predictor variables and an outcome which is penguin body mass.

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth


### Model 1

Model body mass based only on flipper length and bill depth

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients:
model_1

# Pull up stats from test (use p-value for bill_depth_mm in this example)
summary(model_1)       
```
WHAT THIS MEANS (Stats!)

Coefficient: If everything else is held constant, we expect that for each 1 mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average.

P-value: p-value > 0.05 : not statistically significant, accept the null hypothesis, reject the alternative hypothesis

R-squared: 76% of variants in bill depth is explained by this model.



Actually -- we think that a model for penguin mass should contain variables species, flipper length, and penguin sex.

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

# Let's check out the coefficients:
summary(model_2) 
```
Reference levels: species is Adelie (not listed above), sex is female (not listed above)

Species (Gentoo) - If everything else is held constant, on average expect Gentoo penguin to be 836g larger than an Adelie penguin. 

Gender (Male) - If everything else is held constant, on average expect male penguins to be 530g larger than an female penguin. 


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex) +
  scale_fill_manual(values = cal_palette("oak"))
```

### Couple Ways to Get and Report MLR Model Outcomes

```{r}
penguin_model2_coef <- tidy(model_2)
penguin_model2_coef
```

Write inline code `r` that spits out the coefficient (estimate) for Gentoo:

`r penguin_model2_coef$estimate[4]` <- `r` + *dataset* + *$* + *column name* + *[where Gentoo value is in table]*


## Look at Model Diagnostics

Use the plot() function.

```{r}
plot(model_2)
```

## Report Model Outputs in Summary Table

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer:
```{r, results = "asis"}

#Must add the above to code chunk when using stargazer

stargazer(model_2, type = "html")   # Won't look pretty here - used for HTML output of model stats in Knitted doc
```

